\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-11-22 paper/main.tex
revert citep --> cite
re-added pickle incompatibility explanation to beginning of section 3

Across different versions of a given package, particular modules, functions, and other objects 
may be updated, removed, renamed, or otherwise altered in some manner.  In addition to changing the
behaviors of active computations, these changes can render saved objects created using one
version of a package incompatible with other versions of the
same package.  For example, the popular \texttt{pandas}~\cite{McKi10}
library used to include the \texttt{Panel} data structure for storing 3-dimensional arrays.  
Since version 0.20.0, however, the \texttt{Panel} class has been deprecated, and in 
version 0.25.0, it was removed entirely. If a user had a dataset stored in a \texttt{Panel} object
(created using an older version of \texttt{pandas}) and saved it to their disk (e.g., for later reuse
or to share with other users) by serializing the \texttt{Panel} with Python's \texttt{pickle} protocol, 
that dataset could not be read by any version of \texttt{pandas} from 0.25.0 or beyond. These
incompatibilities are also not limited solely to traditional forms of data.
For example, saved model states and other objects may reference
modules, functions, attributes, classes, or other objects that may not be identical (or even present)
across all versions of their associated package.

@@

Next, we load in the reformatted dataset (line 33) and pre-trained
model (line 35) that we wish to use in our analysis.  In our
hypothetical example, we can suppose that the model was provided as a
\texttt{scikit-learn} \texttt{Pipeline} object that passes data
through two pretrained models in succession.  First, a trained \texttt{CountVectorizer}
instance converts text data to an array of word counts.  Second, the
word counts are passed to a topic model~\citep{BleiEtal03} using a
pretrained \texttt{LatentDirichletAllocation} instance.
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/example7}
\end{center}
Let us suppose that the \texttt{Pipeline} object had been saved by its
original creator using the \texttt{joblib} package, as
\texttt{scikit-learn}'s documentation recommends.  Because
\texttt{joblib} uses the \texttt{pickle} protocol internally, the
ability to save and load pre-trained models is not guaranteed across
different \texttt{scikit-learn} versions.  For example, suppose that
the \texttt{Pipeline} object was created using \texttt{scikit-learn}
v0.21.3.  In that version of \texttt{scikit-learn}, the
\texttt{LatentDirichletAllocation} class was defined in
\texttt{sklearn.decomposition.online\_lda}.  However, in version
0.22.0, that module was renamed to \texttt{\_online\_lda}, and in
version 0.22.1, it was again renamed to \texttt{\_lda}.

>>>>

Across different versions of a given package, particular modules, functions, and other objects 
may be updated, removed, renamed, or otherwise altered in some manner.  In addition to changing the
behaviors of active computations, these changes can render saved objects created using one
version of a package incompatible with other versions of the
same package.  For example, the popular \texttt{pandas}~\cite{McKi10}
library used to include the \texttt{Panel} data structure for storing 3-dimensional arrays.  
Since version 0.20.0, however, the \texttt{Panel} class has been deprecated, and in 
version 0.25.0, it was removed entirely. Suppose a user had a dataset stored in a \texttt{Panel} object
(created using an older version of \texttt{pandas}) and had saved it to their disk (e.g., for later reuse
or to share with other users) by serializing the \texttt{Panel} with Python's \texttt{pickle} protocol.
The \texttt{pickle} protocol is a popular choice for persisting data in Python, allowing users to save, share, and load arbitrary objects, though with an important caveat:
In order to successfully ``unpickle'' (i.e., load and restore) a ``pickled'' object, its class must be defined in and importable from the same module as when it was saved.
Thus, because of the \texttt{Panel} class's removal, the user's dataset could not be read by any version of \texttt{pandas} from 0.25.0 or beyond. These
incompatibilities are also not limited solely to traditional forms of data.
For example, saved model states and other objects may reference
modules, functions, attributes, classes, or other objects that may not be identical (or even present)
across all versions of their associated package.

@@

Next, we load in the reformatted dataset (line 33) and pre-trained
model (line 35) that we wish to use in our analysis.  In our
hypothetical example, we can suppose that the model was provided as a
\texttt{scikit-learn} \texttt{Pipeline} object that passes data
through two pretrained models in succession.  First, a trained \texttt{CountVectorizer}
instance converts text data to an array of word counts.  Second, the
word counts are passed to a topic model~\cite{BleiEtal03} using a
pretrained \texttt{LatentDirichletAllocation} instance.
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/example7}
\end{center}
Let us suppose that the \texttt{Pipeline} object had been saved by its
original creator using the \texttt{joblib} package, as
\texttt{scikit-learn}'s documentation recommends.  Because
\texttt{joblib} uses the \texttt{pickle} protocol internally, the
ability to save and load pre-trained models is not guaranteed across
different \texttt{scikit-learn} versions.  For example, suppose that
the \texttt{Pipeline} object was created using \texttt{scikit-learn}
v0.21.3.  In that version of \texttt{scikit-learn}, the
\texttt{LatentDirichletAllocation} class was defined in
\texttt{sklearn.decomposition.online\_lda}.  However, in version
0.22.0, that module was renamed to \texttt{\_online\_lda}, and in
version 0.22.1, it was again renamed to \texttt{\_lda}.
